A load balancing scheme for massively multiplayer online games \thanks{This work was supported by the National Research Council (CNPq) and by the Coordination of Improvement of Higher Education (CAPES), both brazilian research funding agencies.}

### 2009-04-10 trunk/textos/dissertation/MTAP_LaTeX/pub/tex/latex/svjour3/global/balancing.tex

	\item \textbf{Overhead between two regions}: if there is only a server and a region, comprising the entire virtual environment of the game, the use of upload bandwidth of the server will be proportional to the $W_{total}$. However, due to its distribution among various servers, there is the problem of having players from different regions interacting with each other very close to the border between the regions (Figure \ref{fig:interactingregions}). Because of that, each state update of these players' avatars will be sent twice. For example, let $A_i$ be the avatar of the player $P_i$, connected to the server $S_i$, and $A_j$ the avatar of the player $P_j$, connected to the server $S_j$. In order for to $P_i$ interacts with $P_j$, it is necessary that $S_i$ send the state of $A_i$ to $S_j$, which then forwards to $P_j$. The same happens in the other way around. The overhead between regions $R_i$ and $R_j$ is equal, therefore, to the sum of interactions between pairs of cells where each one of them is in one of these regions. If $R_i$ and $R_j$ have respectively $m$ and $n$ cells, we have that the interaction -- or \emph{overhead} -- between them is given by:

>>>>

	\item \textbf{Overhead between two regions}: if there is only one server and one region, comprising the entire virtual environment of the game, the use of the upload bandwidth of the server will be proportional to $W_{total}$. However, due to its distribution among various servers, there is the problem of having players from different regions interacting with each other very close to the border between the regions (Figure \ref{fig:interactingregions}). Because of that, each state update of these players' avatars will be sent twice. For example, let $A_i$ be the avatar of the player $P_i$, connected to the server $S_i$, and $A_j$ the avatar of the player $P_j$, connected to the server $S_j$. In order for $P_i$ to interact with $P_j$, it is necessary that $S_i$ sends the state of $A_i$ to $S_j$, which then forwards to $P_j$. The same happens on the other way around. The overhead between regions $R_i$ and $R_j$ is equal, therefore, to the sum of interactions between pairs of cells where each one of them is in one of these regions. If $R_i$ and $R_j$ have respectively $m$ and $n$ cells, we have that the interaction -- or overhead -- between them is given by:
